### 2015-07-08 narrative/data-reduction.tex
editing 1.3.2

\paragraph{State of the art:} {\bf Data Reduction Techniques} Data compression
broadly consists of three basic steps: (1) Pre-processing to extract as much
structure as feasible. This step is variously referred to as filtering,
preconditioning, and preprocessing but in all cases, the objective is to
represent the data in a form that becomes more amenable to compression.  (2)
Removal of redundancy such as omission of duplicates etc.  Finally, (3) the
resulting data is compressed using entropy coding. The level of compression
that can be achieved in the final step is limited by the Shannon information
content of the data \cite{Gray:book}, and many standard tools are available for
efficient and perfect entropy coding. The potential for compression through
removal of redundancy is generally minor. The main scope for achieving
significant compression (a compression rate of two or better say) therefore
lies in the pre-processing step.

>>>>

\paragraph{State of the art:} {\bf Data Reduction Techniques} Data compression
broadly consists of three basic steps: (1) Pre-processing to extract as much
structure as feasible. This step is variously referred to as filtering,
preconditioning, and preprocessing. But in all cases, the objective is to
represent the data in a form that becomes more amenable to compression.  (2)
Removal of redundancy such as omission of duplicates etc.  Finally, (3) the
resulting data is compressed using entropy coding. The level of compression
that can be achieved in the final step is limited by the Shannon information
content of the data \cite{Gray:book}, and many standard tools are available for
efficient and perfect entropy coding. The potential for compression through
removal of redundancy is generally minor. The main scope for achieving
significant compression (e.g. a compression rate of two) therefore
lies in the pre-processing step.
